Paper without a name

### 2014-05-09 Article.tex
Article.tex modifié

To understand the problem, we first tried manually to get $opt_n$ for very small
values of $n$.\\
For $n=2$, the answer is quite simple~: One box is enough and necessary to swap
the two wires.\\
For $n=3$, two boxes aren't enough. Using a permutation, we can consider that
the first box swap the wires 1 and 2, and that the second box swap the wires 2
and 3.  Then the permutation $(1,3)$ can't be generated with this configuration.
Hence, we have $opt_3=3$.

>>>>

To understand the problem, we first tried manually to get $opt_n$ for very small
values of $n$.\\
For $n=2$, the answer is quite simple~: One box is enough and necessary to swap
the two wires.\\

\begin{figure}
 \centering
 \vspace{+20pt}
 \def\svgwidth{0.15\textwidth}
 \includesvg{svg/2wires_box}
 \caption{Optimal configuration for 2 wires}
\end{figure}

For $n=3$, two boxes aren't enough. Using a permutation, we can consider that
the first box swap the wires 1 and 2, and that the second box swap the wires 2
and 3.  Then the permutation $(1,3)$ can't be generated with this configuration.
Hence, we have $opt_3=3$.

\begin{figure}
 \centering
 \vspace{+20pt}
 \def\svgwidth{0.25\textwidth}
 \includesvg{svg/4wires_box}
 \caption{Valid, but not optimal configuration for 4 wires}
\end{figure}

On these representations, a box is a horizontal line that can swap the wires the points are on.
